Hydra Battles and Cie

### 2020-12-18 doc/part-hydras.tex
correction of typos

Let $(A,<_A)$ and $(B,<_B)$ two well-ordered sets. $A$ and $B$ are said to have \emph{the same order type} if 
there exists a strictly monotonous bijection $b$ from $A$ to $B$, \emph{i.e.} which verifies the proposition
$\forall x\,y\in A, x <_A y \Rightarrow b(x) <_B  b(y)$.

@@

In a set-theoretic framework, one can consider any ordinal $\alpha$ as a well-ordered set, whose  elements are just the ordinals strictly less than $\alpha$, \emph{i.e.} the \emph{segment} $\mathbb{O}_\alpha=[0, \alpha)$. So, one can speak about \emph{finite}, \emph{infinite}, \emph{countable}, etc., ordinals. Nevertheless, since we work within type theory, 
we do not identify ordinals as sets of ordinals, but the correspondance between ordinals and sets of ordinals is the function that maps $\alpha$ to $\mathbb{O}_\alpha$.
For instance $\mathbb{O}_\omega=\mathbb{N}$, and $\mathbb{O}_7=\{0,1,2,3,4,5,6\}$.

@@

Two kinds of representation of ordinals are defined herein.

@@

\section{Countable Ordinals}

Chapter~\ref{chap:schutte} of this document presents an adaptation to \coq{} of an axiomatization in classical logic of the set of countable ordinals by K. Schütte~\cite{schutte}. 
That formalization is quite complex, technical and unshamedly non-constructive,  so we put its description  in the last chapter of this document.

Please note that Schütte considers the (uncountable) set $\mathbb{O}$ of all countable ordinals. This set is well ordered (which is one of Schütte's axioms), and associates to any ordinal $\alpha$ the segment $\mathbb{O}_\alpha$ of all ordinals strictly less than $\alpha$.

In our adaptation to \coq{}, we declare a type \texttt{Ord}, a binary relation \texttt{lt} (with infix notation \texttt{"\_<\_"}, and assume Schütte's axiom. In Chapter~\ref{chap:schutte},
we derive some interesting properties of countable ordinals from these axioms.
It is interesting to compare proofs of a given property (for instance the associativity of addition) in the computational framework of some ordinal notation, and in the axiomatic model of Schütte.

@@

Let $\alpha$ be some (countable) ordinal; 
in \coq{} terms, we call ordinal notation for $\alpha$ a structure composed 
of:
\begin{itemize}
\item A data type $A$ for representing all ordinals strictly below $\alpha$,
\item A well founded order $<$ on $A$, 
\item A correct function for comparing two ordinals. Note  that the reflexive closure of $<$ is thus a \emph{total order}.
\end{itemize}

Such a structure can be proved correct relatively to another ordinal notation or
to Schütte's model.

\subsubsection*{Ordered Types}

The library ~\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Classes.RelationClasses.html}{%
Coq.Classes.RelationClasses} contains some definitions and facts about binary relations, among them strict orders.

@@

The following definitions allow us to make implicit several guessable arguments.
\label{sect:on-lt-notation}
\label{sect:on-le-notation}
\begin{Coqsrc}
Definition on_t  {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := A.

@@

Definition ON_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.
Infix "o<" := ON_lt : ON_scope.

@@

\begin{remark}
The infix notations \texttt{o<} and \texttt{o<=} were defined in order to make apparent the distinction between the various notation scopes that may co-exist in a same statement. So the infix \texttt{<} and \texttt{<=} are reserved to the natural numbers. In the mathematical formulas, however, we still use $<$ and $\leq$ for comparing ordinals.
\end{remark}

@@

The following lemma (together with the type class mechnism) allows us to use simply  measures towards an ordinal notation. It is just an application of  the libraries \texttt{Coq.Wellfounded.Inverse\_Image}
and  \texttt{Coq.Wellfounded.Inclusion}.

@@

The simplest example of ordinal notation is built over the type \texttt{nat} of \coq's standard library. We have only to apply already proven lemmas about Peano numbers.

@@

@@

Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily a total function which merges two lists.

@@

\begin{Coqsrc}
(* adapted from Pascal Manoury et al. *)

Require Import Coq.Program.Wf List.
Require Import FunInd Recdef.

Section Merge.

@@

  - intros; unfold m, measure_lt; cbn; destruct xs0; simpl; left; lia.
  - intros; unfold m, measure_lt; cbn; destruct ys0; simpl; right; lia.
   - auto.
  Defined.

@@

In Sect.~\vref{omega-case}, we proved that there exists no variant towards \texttt{nat}
(\emph{i.e.} the ordinal $\omega$) for proving the termination of all hydra battles.
We  prove now that  the ordinal $\omega^2$ is also insufficient for this purpose.

The proof we are going to develop has exactly the same structure as in Section~\ref{omega-case}.
 Nevertheless, the proof of technical  lemmas is a little more complex, due to 
 the structure of the lexicographic order on $\mathbb{N}\times\mathbb{N}$. 
Consider for instance that there exists an infinite number of ordinals  between
$\omega$ and $\omega\times 2$.

@@

Let us follow the same pattern as in Sect.~\ref{omega-case}.
First, we define an injection $\iota$ from type \texttt{t} into \texttt{Hydra}, by
 associating to  each ordinal $\omega\times i+ j = (i,j)$ the hydra with $i$ branches of length $2$ and
$j$ branches of length $1$.

@@

 In a second step, we build a ``smaller'' hydra.

@@

@@

 \begin{figure}[h]
   \centering
   \begin{tikzpicture}[very thick, scale=0.6]
\begin{scope}[color=blue]
\node (A) at (0,0) {$A$};
\node(A0) at (2,0)[label=below:$0$]{$\bullet$};
\node(A1) at (3,0)[label=below:$1$]{$\bullet$};
\node(A2) at (4,0)[label=below:$2$]{$\bullet$};
\node (Adots) at (6,0) {$\ldots$};
\end{scope}
\begin{scope}[color=red]
\node (B) at (0,2) {$B$};
\node(B0) at (2,2)[label=above:$0$]{$\bullet$};
\node(B1) at (3,2)[label=above:$1$]{$\bullet$};
\node(B2) at (4,2)[label=above:$2$]{$\bullet$};
\node (Bdots) at (6,2) {$\ldots$};
\node (b) at (8,2) [label=above:$b$]{$\bullet$};
\node (bsucc) at (9,2) [label=above:$b+1$]{$\bullet$};
\node (Bdots2) at (10,2) {$\ldots$};
\end{scope}
\begin{scope}[color=red!50!blue]
\draw [->,thin] (A0) -- node [auto] {$\iota$} (B0);
\draw [->,thin] (A1) -- node [auto] {$\iota$} (B1);
\draw [->,thin] (A2) -- node [auto] {$\iota$} (B2);
\draw [->,thin] (Adots) -- node [auto] {$\iota$} (Bdots);
\end{scope}
\end{tikzpicture}
   \caption{\textcolor{blue}{$A$} is a sub-segment  of \textcolor{red}{$B$}}
   \label{fig:subsegment}
 \end{figure}

@@

\subsubsection*{Remark}
\label{sec:orgheadline66}

The name \texttt{T1} we gave to this data-type  is proper to this development and refers
to a hierarchy of ordinal notations. For instance, in~\cite{CantorContrib}, the following type is used to represent ordinals strictly less than \(\Gamma_0\),  in Veblen normal form (see also~\cite{schutte}).

\emph{Please look also at the library
\href{../theories/html/hydras.Gamma0.T2.html}{Gamma0.T2.html}}.

\begin{Coqsrc}
Inductive T2 : Set :=
  zero : T2
| gcons : T2 -> T2 -> nat -> T2 -> T2.
\end{Coqsrc}

@@

\subsubsection{The Ordinal \(\omega^\alpha\), a.k.a. \(\phi_0(\alpha)\)}
\label{sec:orgheadline70}

We provide also a notation for ordinals of the form $\omega^\alpha$.

\label{sect:notation-phi0}

@@

The ordinal $\epsilon_0$, although not represented by a finite term in Cantor normal form, is approximed by the sequence of $\omega$-towers (see also Sect~\vref{sect:epsilon0-as-limit} ).

@@

\label{Predicates:lt-T1}
Please note that this definition of \texttt{lt} makes it easy to write proofs by reflection, as shown by the following exampgles.

@@

Note that the order \texttt{lt} is not reflected 
in the structure (size and/or height) of the terms of \texttt{T1}. 
For instance the ordinal of Fig \ref{fig:cnf-example} is strictly less
than the structurally simpler \(\omega^{\omega^\omega}\times 2\).

@@

This term would have been written \(\omega^1\times 2 + \omega^\omega \times 3\) in the usual mathematical notation. We note that the exponents of $\omega$ are not in the right (strictly decreasing) order.

With the help of the order \texttt{lt} on \texttt{T1}, we are now able to characterize
the set of all well-formed ordinal terms:

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#nf_b}{Epsilon0.T1}}

@@

\index{Exercises}
\begin{exercise}
In earlier versions of this development, the predicate \texttt{nf} was defined  inductively, with various constructors describing all possible cases.
\begin{enumerate}
\item Please give such a definition, in a dedicated module.
\item Prove the logical equivalence between your definition and ours.
\item Define a variant of the type \texttt{E0} (with your definition of \texttt{nf}).
\item Can you still prove a lemma like \texttt{E0\_eq\_iff} ? With the help of an axiom from some module of the standard library ?
\end{enumerate}
\end{exercise}
For upgrading constants and fonctions of \texttt{T1}, we have to prove that 
the term they build is in normal form.
For instance, let us represent the ordinals $0$ and $\omega$ as instances of the class \texttt{E0}.

@@

Pattern matching and structural recursion allow us to define the notions of successor and limit ordinal with the help of  boolean functions on type \texttt{T1}.

 \vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#succb}{Epsilon0.T1}}

\begin{Coqsrc}
  Fixpoint succb alpha :=
  match alpha with
      zero => false
    | ocons zero _ _ => true
    | ocons alpha n beta => succb beta
  end.

Fixpoint limitb alpha :=
  match alpha with
      zero => false
    | ocons zero _ _ => false
    | ocons alpha n zero => true
    | ocons alpha n beta => limitb beta
  end.
\end{Coqsrc}

@@

@@

\begin{Coqsrc}
Instance plus (alpha beta : E0) : E0.
Proof.
  refine (@mkord (T1.plus (@cnf alpha) (@cnf beta))_ );
    apply plus_nf; apply cnf_ok.
Defined.

@@

\index{Exercises}
 \begin{exercise}
Let $\alpha$ be an ordinal. We say that $\alpha$ is \emph{infinite} iff the segment $[0,\alpha)$ is an infinite set. 
\begin{enumerate}
\item Adapt this definition to the type \texttt{E0}.
\item Prove that \emph{being infinite} is decidable on type \texttt{E0}.
\item Prove that $\alpha$ is infinite if and only if for all finite ordinal $i$,
$i+\alpha=\alpha$.
\end{enumerate}
 \end{exercise}

@@

Let \texttt{n:nat} and \texttt{beta:T1} such that \texttt{ocons alpha n beta} is in normal form. 
We prove first that \texttt{beta} is accessible,  which allows us to by well-founded induction on \texttt{beta}, 
and natural induction on \texttt{n}, that (\texttt{ocons alpha n beta}) is accessible.
The proof, quite long, can be consulted in \url{../theories/html/hydras.Epsilon0.T1.html}

>>>>

Let $(A,<_A)$ and $(B,<_B)$ two well-ordered sets. $A$ and $B$ are said to have \emph{the same order type} if 
there exists a strictly monotonous bijection $b$ from $A$ to $B$, \emph{i.e.} which verifies the proposition
$\forall x\,y\in A,\, x <_A y \Rightarrow b(x) <_B  b(y)$.

@@

In a set-theoretic framework, one can consider any ordinal $\alpha$ as a well-ordered set, whose  elements are just the ordinals strictly less than $\alpha$, \emph{i.e.} the \emph{segment} $\mathbb{O}_\alpha=[0, \alpha)$. So, one can speak about \emph{finite}, \emph{infinite}, \emph{countable}, etc., ordinals. Nevertheless, since we work within type theory, 
we do not identify ordinals as sets of ordinals, but consider the correspondance between ordinals and sets of ordinals as the function that maps $\alpha$ to $\mathbb{O}_\alpha$.
For instance $\mathbb{O}_\omega=\mathbb{N}$, and $\mathbb{O}_7=\{0,1,2,3,4,5,6\}$.

@@

Two kinds of representation of ordinals are defined in our development.

@@

% \section{Countable Ordinals}

% Chapter~\ref{chap:schutte} of this document presents an adaptation to \coq{} of an axiomatization in classical logic of the set of countable ordinals by K. Schütte~\cite{schutte}. 
% That formalization is quite complex, technical and unshamedly non-constructive,  so we put its description  in the last chapter of this document.

% Please note that Schütte considers the (uncountable) set $\mathbb{O}$ of all countable ordinals. This set is well ordered (which is one of Schütte's axioms), and associates to any ordinal $\alpha$ the segment $\mathbb{O}_\alpha$ of all ordinals strictly less than $\alpha$.

% In our adaptation to \coq{}, we declare a type \texttt{Ord}, a binary relation \texttt{lt} (with infix notation \texttt{"\_<\_"}, and assume Schütte's axiom. In Chapter~\ref{chap:schutte},
% we derive some interesting properties of countable ordinals from these axioms.

It is interesting to compare proofs of a given property (for instance the associativity of addition) both in the computational framework of some ordinal notation, and in the axiomatic model of Schütte.

@@

Let $\alpha$ be some (countable) ordinal; 
in \coq{} terms, we call \emph{ordinal notation for $\alpha$} a structure composed 
of:
\begin{itemize}
\item A data type $A$ for representing all ordinals strictly below $\alpha$,
\item A well founded order $<$ on $A$, 
\item A correct function for comparing two ordinals. Note  that the reflexive closure of $<$ is thus a \emph{total order}.
\end{itemize}

Such a structure can be proved correct relatively to a bigger ordinal notation or
to Schütte's model.

First, we import the definition of strict orders from
the library ~\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Classes.RelationClasses.html}{%
Classes.RelationClasses}, 
and the inductive specification of a comparison from
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Init.Datatypes.html}{%
Init.Datatypes}.

@@

%The following definitions allow us to make implicit several guessable arguments.
\label{sect:on-lt-notation}
\label{sect:on-le-notation}
\begin{Coqsrc}
Definition on_t  {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare} := A.

@@

Definition ON_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.

Infix "o<" := ON_lt : ON_scope.

@@

\begin{remark}
The infix notations \texttt{o<} and \texttt{o<=} are defined in order to make apparent the distinction between the various notation scopes that may co-exist in a same statement. So the infix \texttt{<} and \texttt{<=} are reserved to the natural numbers. In the mathematical formulas, however, we still use $<$ and $\leq$ for comparing ordinals.
\end{remark}

@@

The following lemma (together with the type class mechnism) allows us to define termination measures over any ordinal notation. It is just an application of  the libraries \texttt{Coq.Wellfounded.Inverse\_Image}
and  \texttt{Coq.Wellfounded.Inclusion}.

@@

The simplest example of ordinal notation is built over the type \texttt{nat} of \coq's standard library. We just have to apply already proven lemmas about Peano numbers.

@@

\begin{Coqsrc}
Lemma lt_wf : well_founded lt.
Proof. 
  destruct NA, NB; apply wf_disjoint_sum; [apply wf | apply wf0].
Qed.
\end{Coqsrc}

Then, we register an instance of \texttt{ON}:

@@

Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily a total function which merges two lists (example contributed by Pascal Manoury).

@@

\begin{Coqsrc}
Section Merge.

@@

  - intros; unfold m, measure_lt; cbn; destruct xs0; simpl; left; lia.
  - intros; unfold m, measure_lt; cbn; destruct ys0; simpl; right; lia.
  - apply wf_measure.
  Defined.

@@

In Sect.~\vref{omega-case}, we proved that there exists no variant from \texttt{Hydra} to \texttt{(nat,$<$)}
(\emph{i.e.} the ordinal $\omega$) for proving the termination of all hydra battles.
We  prove now that  the ordinal $\omega^2$ is also insufficient for this purpose.

The proof we are going to comment has exactly the same structure as in Section~\ref{omega-case}.
 Nevertheless, the proof of technical  lemmas is a little more complex, due to 
 the structure of the lexicographic order on $\mathbb{N}\times\mathbb{N}$. 
Consider for instance that there exists an infinite number of ordinals  between
$\omega$ and $\omega\times 2$.

@@

We  follow the same pattern as in Sect.~\ref{omega-case}.
First, we define an injection $\iota$ from type \texttt{t} into \texttt{Hydra}, by
 associating to  each ordinal $\omega\times i+ j = (i,j)$ the hydra with $i$ branches of length $2$ and
$j$ branches of length $1$.

@@

 In a second step, we build a ``smaller'' hydra\footnote{With respect to the measure $m$.}.

@@

\begin{figure}[h]
   \centering
   \begin{tikzpicture}[very thick, scale=0.6]
\begin{scope}[color=blue]
\node (A) at (0,0) {$A$};
\node(A0) at (2,0)[label=below:$0$]{$\bullet$};
\node(A1) at (3,0)[label=below:$1$]{$\bullet$};
\node(A2) at (4,0)[label=below:$2$]{$\bullet$};
\node (Adots) at (6,0) {$\ldots$};
\end{scope}
\begin{scope}[color=red]
\node (B) at (0,2) {$B$};
\node(B0) at (2,2)[label=above:$0$]{$\bullet$};
\node(B1) at (3,2)[label=above:$1$]{$\bullet$};
\node(B2) at (4,2)[label=above:$2$]{$\bullet$};
\node (Bdots) at (6,2) {$\ldots$};
\node (b) at (8,2) [label=above:$\alpha$]{$\bullet$};
\node (bsucc) at (9,2) [label=above:$\alpha+1$]{$\bullet$};
\node (Bdots2) at (10,2) {$\ldots$};
\end{scope}
\begin{scope}[color=red!50!blue]
\draw [->,thin] (A0) -- node [auto] {$\iota$} (B0);
\draw [->,thin] (A1) -- node [auto] {$\iota$} (B1);
\draw [->,thin] (A2) -- node [auto] {$\iota$} (B2);
\draw [->,thin] (Adots) -- node [auto] {$\iota$} (Bdots);
\end{scope}
\end{tikzpicture}
   \caption{\textcolor{blue}{$A$} is a sub-segment  of \textcolor{red}{$B$}}
   \label{fig:subsegment}
 \end{figure}

@@

@@

\paragraph{Remark}
The name \texttt{T1} we gave to this data-type  is proper to this development and refers
to a hierarchy of ordinal notations. For instance, in Library \href{../theories/html/hydras.Gamma0.T2.html}{Gamma0.T2},  the following type is used to represent ordinals strictly less than \(\Gamma_0\),  in Veblen normal form (see also~\cite{schutte}).
\noindent
\begin{Coqsrc}
Inductive T2 : Set :=
  zero : T2
| gcons : T2 -> T2 -> nat -> T2 -> T2.
\end{Coqsrc}

@@

\subsubsection{The Ordinal \(\omega^\alpha\), a.k.a. \(\phi_0(\alpha)\)}
\label{sect:notation-phi0}
We provide also a notation for ordinals of the form $\omega^\alpha$.

@@

The ordinal $\epsilon_0$, although not represented by a finite term in Cantor normal form, is approximated by the sequence of $\omega$-towers (see also Sect~\vref{sect:epsilon0-as-limit} ).

@@

\label{Predicates:lt-T1}
Please note that this definition of \texttt{lt} makes it easy to write proofs by computation, as shown by the following examples.

@@

Note that the order \texttt{lt} is not reflected 
in the structure (size and/or height) of the terms of \texttt{T1}.

\begin{Coqsrc}
Example Ex0:
  lt (ocons (phi0 (phi0 omega)) 2
            (ocons (phi0 10) 33
                   (ocons (phi0 9) 63 zero)))
     (ocons  (phi0 (phi0 omega)) 2 (phi0 (phi0 11))).
Proof.
  reflexivity. 
Qed.
\end{Coqsrc}

@@

This term would have been written \(\omega^1\times 2 + \omega^\omega \times 3\) in the usual mathematical notation. We note that the exponents of $\omega$ are not in the right (strictly decreasing) order.
Nevertheless, with the help of the order \texttt{lt} on \texttt{T1}, we are now able to characterize
the set of all well-formed ordinal terms:

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#nf_b}{Epsilon0.T1}}

@@

\index{Exercises}
\begin{exercise}
In earlier versions of this development, the predicate \texttt{nf} was defined  inductively, with various constructors describing all possible cases.
\begin{enumerate}
\item Please give such a definition, in a dedicated module.
\item Prove the logical equivalence between your definition and ours.
\item Define a variant of the type \texttt{E0} (with your definition of \texttt{nf}).
\item Can you still prove a lemma like \texttt{E0\_eq\_iff} ? With the help of an axiom from some module of the standard library ?
\end{enumerate}
\end{exercise}

In order to  upgrade constants and fonctions from type \texttt{T1} to \texttt{E0}, we have to prove that 
the term they build is in normal form.
For instance, let us represent the ordinals $0$ and $\omega$ as instances of the class \texttt{E0}.

@@

Pattern matching and structural recursion allow us to define boolean characterizations  of successor and limit ordinals.

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#succb}{Epsilon0.T1}}

\begin{Coqsrc}
Fixpoint succb (alpha:T1) : bool :=
  match alpha with
    | zero => false
    | ocons zero _ _ => true
    | ocons alpha n beta => succb beta
  end.

Fixpoint limitb (alpha : T1) : bool :=
  match alpha with
    | zero => false
    | ocons zero _ _ => false
    | ocons alpha n zero => true
    | ocons alpha n beta => limitb beta
  end.
\end{Coqsrc}

@@

The function \texttt{succ} is related with addition through the following lemma:

\begin{Coqsrc}
Lemma succ_is_plus_one (alpha : T1) :  succ alpha = alpha + 1.
Proof.
  induction alpha as [|a IHa n b IHb].
  (* ... *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma plus_nf : forall a,  nf a -> forall b, nf b -> nf (a + b).
Proof.
 (* ... *)

Instance plus (alpha beta : E0) : E0.
Proof.
  refine (@mkord (T1.plus (@cnf alpha) (@cnf beta))_ );
    apply plus_nf; apply cnf_ok.
Defined.

@@

\begin{remark}
In all this development, two representations of ordinals co-exist: ordinal terms (type \texttt{T1}, notation scope \texttt{t1\_scope}, for reasoning on the tree-structure of Cantor normal forms), and ordinal terms \emph{known to be in normal form} (type \texttt{E0}, notation scope \texttt{E0\_scope}). Looking at the contexts displayed by \coq{} prevents you from any risk of confusion.
\end{remark}

\index{Exercises}
 \begin{exercise}
Let $\alpha$ be an ordinal. We say that $\alpha$ is \emph{infinite} iff the segment $[0,\alpha)$ is an infinite set. 
\begin{enumerate}
\item Adapt this definition to the type \texttt{E0}.
\item Prove that \emph{being infinite} is decidable on type \texttt{E0}.
\item Prove that $\alpha$ is infinite if and only if for any finite ordinal $i$,
$i+\alpha=\alpha$.
\end{enumerate}
 \end{exercise}

@@

Let \texttt{n:nat} and \texttt{beta:T1} such that \texttt{ocons alpha n beta} is in normal form. 
We prove first that \texttt{beta} is accessible,  which allows us to prove by well-founded induction on \texttt{beta}, 
and natural induction on \texttt{n}, that (\texttt{ocons alpha n beta}) is accessible.
The proof, quite long, can be consulted in \url{../theories/html/hydras.Epsilon0.T1.html}
